Detecting threats of violence in YouTube comments

### 2016-03-03 submission.tex
Changed some formatting

\usepackage{xytree} % Dependency tree

@@

\section{The YouTube threat data set}
\label{sec:data}
The YouTube threat data set is comprised of user-written comments from
eight different YouTube videos \cite{hammer2014}. A comment
consists of a set of sentences, each of them manually annotated to be
either a \tov{} (or support for a \tov{}) or not. The data set
furthermore records the username\footnote{In 2013, YouTube changed its
  commenting system from using unique usernames, to using "real
  names", like Facebook and other sites \cite{youtube2013}. Some
  accounts, however, did not provide real names, so they continue to
  only be identified by their usernames.} of the user that posted the
comment. The eight videos that the comments were posted to cover religious and political topics like halal slaughter, immigration,
Anders Behring Breivik, Jihad, etc. \cite{hammer2014}. 
%The videos cover slightly different topics, the videos all contain the same
%type of discussions, namely of xenophobia and racism.

@@

\begin{figure}
\begin{verbatim}
timpa666
1    and i will kill every
     fucking muslim and arab!

NimsXdimensions
0    Need a solution?
1    Drop one good ol' nuke on
     that black toilet in Mecca.

Ammar Alozaibi
1    Funny, We will conquer you
     all in just few years, U will
     be my slave and your women
     will be my Sex Toy in Bed.

\end{verbatim}
\caption{Examples of comments from the data set.}
\label{fig:comments}
\end{figure}

>>>>

\usepackage{xytree} % Dependency tree
\usepackage{fancyvrb} % Comments verbatim

@@

\section{The YouTube threat data set}
\label{sec:data}
The YouTube threat data set is comprised of user-written comments from
eight different YouTube videos \cite{hammer2014}. A comment
consists of a set of sentences, each of them manually annotated to be
either a \tov{} (or support for a \tov{}) or not. The data set
furthermore records the username\footnote{The usernames were annonymized by us}
%% \footnote{In 2013, YouTube changed its
%%   commenting system from using unique usernames, to using "real
%%   names", like Facebook and other sites \cite{youtube2013}. Some
%%   accounts, however, did not provide real names, so they continue to
%%   only be identified by their usernames.}
  of the user that posted the
comment. The eight videos that the comments were posted to cover religious and political topics like halal slaughter, immigration,
Anders Behring Breivik, Jihad, etc. \cite{hammer2014}. 
%The videos cover slightly different topics, the videos all contain the same
%type of discussions, namely of xenophobia and racism.

@@

\begin{figure}
\begin{Verbatim}[fontsize=\small]
User #44
1    and i will kill every
     fucking muslim and arab!

User #88
0    Need a solution?
1    Drop one good ol' nuke on
     that black toilet in Mecca.

User #138
1    Funny, We will conquer you
     all in just few years, U will
     be my slave and your women
     will be my Sex Toy in Bed.
\end{Verbatim}
\caption{Examples of comments from the data set.}
\label{fig:comments}
\end{figure}
